Multi-level modeling with Openflexo/\FML

### 2021-09-27 9-relatedworks.tex

A plethora of multi-level modeling approaches and tools with different foundations have appeared in recent years\footnote{\url{https://homepages.ecs.vuw.ac.nz/Groups/MultiLevelModeling/MultiTools}}. Comparing them lies out of the scope of this paper. In this sense, we limit the following discussion to the presentation and comparison of previous solutions to the MULTI Process Challenge.

>>>>

A plethora of multi-level modeling approaches and tools\footnote{\url{https://homepages.ecs.vuw.ac.nz/Groups/MultiLevelModeling/MultiTools}} with different foundations have appeared in recent years~\citep{somogyi2021playground}. Comparing them lies out of the scope of this paper. In this sense, we limit the following discussion to the presentation and comparison of previous solutions to the MULTI Process Challenge.
